Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-11 paper/disc20clustering.tex
Consistency

\noindent
\textbf{Learning model.}
We study a variant of Online Balanced Partitioning,
where the communication pattern is \emph{static}:
whether a pair of  nodes ever communicate or not, 
is determined a priori and is unknown to algorithms,
 and requests to such pairs arrive indefinitely.
Any algorithm must eventually collocate  pairs of communicating nodes,
as otherwise it cannot be competitive.
As in Henzinger et al. \cite{sigmetrics19_partitioning}, we assume that the communication graph admits a \emph{perfect partition},
i.e., a partition in which no inter-cluster request ever occurs.
%any algorithm must learn this perfect partition.
The algorithm's objective is to \emph{learn} the (static) communication graph
 while serving all requests,
and without executing too many migrations.
For the learning model, we  assume that the migration cost is $\alpha=1$.

>>>>

\noindent
\textbf{Learning model.}
We study a \emph{learning} variant of dynamic balanced graph partitioning,
where the communication pattern is \emph{static}:
whether a pair of  nodes ever communicate or not, 
is determined a priori and is unknown to algorithms,
 and requests to such pairs arrive indefinitely.
Any algorithm must eventually collocate  pairs of communicating nodes,
as otherwise it cannot be competitive.
As in Henzinger et al. \cite{sigmetrics19_partitioning}, we assume that the communication graph admits a \emph{perfect partition},
i.e., a partition in which no inter-cluster request ever occurs.
%any algorithm must learn this perfect partition.
The algorithm's objective is to \emph{learn} the (static) communication graph
 while serving all requests,
and without executing too many migrations.
For the learning model, we  assume that the migration cost is $\alpha=1$.
